\vspace{24pt} Comparison of Different Data Layouts for Columnar In-Memory Databases on the Basis of an Example Application

### 2018-08-31 paper/paper.tex
add benchmark: time and coordinate range

\subsubsection{Get taxis in time and range boundary}

>>>>

\subsubsection{Get taxis in time and range boundary}
We wanted to find out how these last two optimizations perform on a more complex query of a realistic scenario: retrieving all taxis within a defined time period and geografic bounding rectangle. We implemented this rather complex statement as prcedure for easy usage. Figure \ref{fig:bench_time_range_boundary} shows that the execution time of the multiple columns approach dramatically exceeds the single column approach with increasing number of results.
\begin{figure}[ht]
  \centering
  \includegraphics[width=0.48\textwidth]{img/bench_time_range_boundary.png}
  \caption{Time in ms required for filtering by coordinates and time}
  \label{fig:bench_time_range_boundary}
\end{figure}
